---
title: "Longitudinal TTU"
author: "Matthew Hamilton"
date: "26/01/2021"
output: html_document
---

## Longitudinal mapping models

Regression coefficients of the baseline score and score changes (from baseline to follow-up) estimated in individual `r get_lngl_ttu_types(results_ls)` models are summarised in `r make_indpnt_predrs_lngl_tbls_ref(params_ls)`.<!-- Table end --> Bayesian R^2^ from each model is reported. Modelled residual standard deviations (SDs) were also provided to support simulation studies which need to capture individual level variation. `r  make_lngl_ttu_r2_text(results_ls, part_int = 1:2) %>% stringr::str_replace("0.68 ","0.680 ")`. Variance of the random intercept was comparable with the residual variance.  

```{r, child = "MS_Results_Ratios.Rmd", echo=FALSE}
```

Distribution of observed and predicted utility scores and their association from GLMM (Gaussian distribution with log link) and LMM (c-loglog transformed)  using `r get_prefd_mdl_predrs(results_ls)` are plotted in Figure \@ref(fig:fig2). Compared with GLMM, the predicted utility scores from the LMM model converge better to the observed distribution and provide better estimations at the tail of the distribution. When the observed utility scores were low, the predicted utility were too high in the GLMM model, see Figure 2 (B). The observed and predicted distributions of utility scores for other anxiety and depression measurements were similar from LMM models. However, GLMM models had low coverage in utility scores below 0.3 and also made predictions out of range (over 1).

We also evaluated models with SOFAS at baseline and SOFAS change from baseline added to psychological distress, depression and anxiety predictors (Online Resource, `r ifelse(params$output_type_1L_chr=="Word","","Tables")` A.3 and A.4). SOFAS scores were generally found to be associated with utility scores when controlling for anxiety and depression symptom measurements in longitudinal models. 

Detailed summaries of all models from the primary and secondary analyses are available in the online data repository (see "Code and data availability").

```{r, child = child_figs_ls$fig2, echo=FALSE}
```
