---
title: "MA_Results"
author: "Matthew Hamilton"
date: "13/10/2020"
output: html_document
---

```{r child="MS_Tables.Rmd", echo=FALSE}
```
```{r child="MS_Figures.Rmd", echo=FALSE}
```
```{r child="MS_Results_Cohort.Rmd", echo=FALSE}
```
```{r child="MS_Results_HU_And_Predrs.Rmd", echo=FALSE}
```
```{r child="MS_Results_TTU_Mdl_Perf.Rmd", echo=FALSE}
```
```{r child="MS_Results_Lngtl_TTU.Rmd", echo=FALSE}
```
##	Toolkits 
To aid study replication, we created a unified R program that performs all steps from raw data ingest, data pre-processing, utility scoring, model specification and testing, creation and documenting of shareable outputs, dissemination of study outputs and authoring of a draft manuscript [@hamilton_matthew_2022_6129906]. To facilitate more generalised use of parts of our study analysis and reporting algorithms, we distributed the code to run program sub-routines as development version R packages for describing and validating input data [@hamilton_matthew_2022_6084467], scoring health utility data [@hamilton_matthew_2022_6084824], specifying and testing mapping models [@hamilton_matthew_2022_6116701] and reporting mapping studies [@gao_caroline_2022_6130155].

To facilitate appropriate use of the mapping models we developed we created catalogues with detailed information about the performance of all models generated by our study under multiple types of regime (e.g. whether: mean or sampled parameter values are used; minimum and maximum constraints are applied to prediction results; the original R model objects or just tables of model coefficients are used). We distribute these results in an online data repository [@DVN/DKDIB0_2021] along with instructions about our mapping models can be used to make predictions with new data using another R package [@matthew_p_hamilton_2021_5646669] that we developed.  
