---
title: "Untitled"
author: "Matthew Hamilton"
date: "26/01/2021"
output: html_document
---

## `r get_hlth_utl_nm(results_ls)` and candidate predictors
Distribution of `r get_hlth_utl_nm(results_ls)` total utility score and sub-domain scores are displayed in Figure \@ref(fig:fig1). The mean utility score at baseline is `r get_hlth_utl_stat(results_ls, stat_1L_chr = "bl_mean")` (SD = `r get_hlth_utl_stat(results_ls, stat_1L_chr = "bl_sd")`) and is `r get_hlth_utl_stat(results_ls, stat_1L_chr = "fup_mean")` (SD = `r get_hlth_utl_stat(results_ls, stat_1L_chr = "fup_sd")`) at follow-up. Distribution of candidate predictors,  K6, BADS, PHQ-9, GAD-7, OASIS and SCARED, `r ifelse(get_nbr_of_predrs(results_ls, as_words_1L_lgl = F)>1,"are","is")` summarised in `r ifelse(params_ls$output_type_1L_chr=="Word","","Table")` \@ref(tab:predrscors). `r make_correlation_text(results_ls) %>% stringr::str_sub(end=-2)`, although all correlation coefficients can be characterised as being strong. 

```{r, child = child_docs_ls$Predrs_Cors, echo=FALSE}
```
```{r, child = child_figs_ls$fig1, echo=FALSE}
```
